INTELLIGENT SYSTEMS

### 2021-04-23 papers/paper_8.tex
finish slides of paper8
finish 9.3
some fixes

\subsection{INTRODUCTION}
The goal of visual tracking systems is to be able to obtain the position of 
the tracked target even in subsequent frames. The problems to be solved are 
those of occlusion, background clutter, illumination variations, deformation 
etc. The existing state-of-the-art models carry out training online exclusively. 
Some methods, based on pre-trained convolutional networks (CNN), track 
the object based on the background. In these networks, stochastic gradient 
descent is applied in order to update the entire network. However, these 
models appear to be too slow and do not work well in real-time. The following 
paper uses a model that compares similarities and is trained offline in order to 
predict the patch present in the next frame. The method, thanks to the use of 
the relative distance, is robust in the presence of phenomena that introduce 
the so called distractors. The purpose is to be able to compare the patch that 
identifies the target template (the object) with all the possible positions 
of the same region belonging to the next frame. In addition to tracking the 
object, the proposed model is a framework for EMDSLT tracking like the 
one shown in figure \ref{fig:EMDSLT}. Within it, two procedures are considered important: 
updating the model and self-recovery from failures. The network is composed 
of two types of structures, one that is responsible for dast-speed verification 
and production of the tracking results, while the second is responsible for re-verification 
and re-detection of the target object on the patches previously 
generated.
\begin{figure}[h!]
    \centering
    \includegraphics[width = \linewidth]{images/paper8/EMDSLT.png}
    \centering
    \caption{The framework of EMDSLT proposed method.}
    \label{fig:EMDSLT}
\end{figure}.

@@

\subsubsection{Result and Analysis}
\begin{enumerate}
    \item \emph{Comparison with Recent Real-Time Trackers}: the performance of each tracker, including the one proposed, is shown below. For the OTB dataset, several metrics are used to evaluate its tracking quality. Among these metrics we have those of AUC and precision, while for the VOT dataset the metrics specified above are used (Fig.\ref{fig:PerfComp}).
    \begin{figure}[h!]
        \centering
        \includegraphics[width = \linewidth]{images/paper8/metrics.png}
        \centering
        \caption{Performance comparison with Recent Real-Time Trackers}
        \label{fig:PerfComp}
    \end{figure}
    \item \emph{Attribute-Based Evaluation}: the presence of distracting elements leads 
    many methods to fail to track them. In figure \ref{fig:AUCScore} it is possible to see the 
    comparison, in terms of AUC score, reached by different methods on 
    the OTB-2013 dataset, when these elements are present. The values 
    in blue are the highest and are obtained from the best method, while 
    those in red are placed in second position.
    \begin{figure}[h!]
        \centering
        \includegraphics[width = \linewidth]{images/paper8/AUC.png}
        \centering
        \caption{AUC score on OTB-2013 dataset.}
        \label{fig:AUCScore}
    \end{figure}
    \item \emph{Qualitative Evaluation}: The use of the Template-Searching-Background (TSB), allows you to use the background patches to train the model (Fig.\ref{fig:TSBMin}). This method helps to minimize the relative distance $d(\cdot)$ (\ref{distanceFunc}) which translated into other words means bringing the target template closer to the $X_i^+$ samples and at the same time moving the background distractors $B_i$ away from the positive sample. This method allows for better performance than existing state-of-the-art models. A visual example of comparison of the trackers made by the different methods, including the one proposed, is visible in figure \ref{fig:qualitativeTracking}.
    \begin{figure}[h!]
        \centering
        \includegraphics[width = \linewidth]{images/paper8/TSB.png}
        \centering
        \caption{Template-Searching-Background to minimizes the relative distance.}
        \label{fig:TSBMin}
    \end{figure}
    \begin{figure}[h!]
        \centering
        \includegraphics[width = \linewidth]{images/paper8/qualitative.png}
        \centering
        \caption{Qualitative reuslt of seven trackers. The bounding box with an orange dotted line shows the ground-truth localization of the target object.}
        \label{fig:qualitativeTracking}
    \end{figure}
\end{enumerate}

\subsection{CONCLUSION}
The proposed framework, from the results obtained in the benchmarks, seems 
to be the best. The achievement of these results were possible thanks to the 
integration of a verification and detecting method. The use of the TSB 
method was fundamental, which, by reducing the relative distance between 
the various patches, allowed for good model learning.

>>>>

\subsection{INTRODUCTION}
The goal of visual tracking systems is to be able to obtain the position of 
the tracked target even in subsequent frames. The problems to be solved are 
those of occlusion, background clutter, illumination variations, deformation 
etc. The existing state-of-the-art models carry out training online exclusively. 
Some methods, based on pre-trained convolutional networks (CNN), track 
the object based on the background. In these networks, stochastic gradient 
descent is applied in order to update the entire network. However, these 
models appear to be too slow and do not work well in real-time. The following 
paper uses a model that compares similarities and is trained offline in order to 
predict the patch present in the next frame. The method, thanks to the use of 
the relative distance, is robust in the presence of phenomena that introduce 
the so called distractors. The purpose is to be able to compare the patch that 
identifies the target template (the object) with all the possible positions 
of the same region belonging to the next frame. In addition to tracking the 
object, the proposed model is a framework for EMDSLT tracking like the 
one shown in figure \ref{fig:EMDSLT}. Within it, two procedures are considered important: 
updating the model and self-recovery from failures. The network is composed 
of two types of structures, one that is responsible for dast-speed verification 
and production of the tracking results, while the second is responsible for re-verification 
and re-detection of the target object on the patches previously 
generated.
\begin{figure}[h!]
    \centering
    \includegraphics[width = \linewidth]{images/paper8/EMDSLT.png}
    \centering
    \caption{The framework of EMDSLT proposed method.}
    \label{fig:EMDSLT}
\end{figure}

@@

\subsubsection{Result and Analysis}
\begin{enumerate}
    \item \emph{Comparison with Recent Real-Time Trackers}: the performance of each tracker, including the one proposed, is shown below. For the OTB dataset, several metrics are used to evaluate its tracking quality. Among these metrics we have those of AUC and precision, while for the VOT dataset the metrics specified above are used (Fig.\ref{fig:PerfComp}).
    \begin{figure}[h!]
        \centering
        \includegraphics[width = \linewidth]{images/paper8/metrics.png}
        \centering
        \caption{Performance comparison with Recent Real-Time Trackers}
        \label{fig:PerfComp}
    \end{figure}
    \item \emph{Attribute-Based Evaluation}: the presence of distracting elements leads 
    many methods to fail to track them. In figure \ref{fig:AUCScore} it is possible to see the 
    comparison, in terms of AUC score, reached by different methods on 
    the OTB-2013 dataset, when these elements are present. The values 
    in red are the highest and are obtained from the best method, while 
    those in blue are placed in second position.
    \begin{figure}[h!]
        \centering
        \includegraphics[width = \linewidth]{images/paper8/AUC.png}
        \centering
        \caption{AUC score on OTB-2013 dataset.}
        \label{fig:AUCScore}
    \end{figure}
    \item \emph{Qualitative Evaluation}: The use of the Template-Searching-Background 
    (TSB), allows you to use the background patches to train the model 
    (Fig.\ref{fig:TSBMin}). This method helps to minimize the relative distance $d(\cdot)$ (\ref{distanceFunc}) 
    which translated into other words means bringing the target template 
    closer to the $X_i^+$ samples and at the same time moving the background 
    distractors $B_i$ away from the positive sample. This method allows for 
    better performance than existing state-of-the-art models. A visual example 
    of comparison of the trackers made by the different methods, 
    including the one proposed, is visible in figure \ref{fig:qualitativeTracking}.
    \begin{figure}[h!]
        \centering
        \includegraphics[width = \linewidth]{images/paper8/TSB.png}
        \centering
        \caption{Template-Searching-Background to minimizes the relative distance.}
        \label{fig:TSBMin}
    \end{figure}
    \begin{figure}[h!]
        \centering
        \includegraphics[width = \linewidth]{images/paper8/qualitative.png}
        \centering
        \caption{Qualitative reuslt of seven trackers. The bounding box with an orange dotted line shows the ground-truth localization of the target object.}
        \label{fig:qualitativeTracking}
    \end{figure}
\end{enumerate}

\subsection{CONCLUSION}
The proposed framework, from the results obtained in the benchmarks, seems 
to be the best in solving the problem of distractors. The achievement of these 
results were possible thanks to the integration of a verification and detecting 
method. The use of the TSB method was fundamental, which, by reducing 
the relative distance between the various patches, allowed for good model 
learning.
